We are not the 99 percent: quantifying bright satellite distributions in the Local Group

### 2017-11-02 paper/paper.tex
+1 paragraph

We find 27 pairs with these conditions. 
We then select the pairs where in both halos there are at least 15
detected subhalos, thus discarding pairs with halos with the lowest
mass.
We end up with a total of 20 pairs that fulfill these criteria,
Appendix A shows the physical  properties (stellar masses, maximum
circular velocities, radial velocities and separation) in those pairs.

@@

@@

This

>>>>

We find 27 pairs with these conditions. 
We then select the pairs where in both halos there are at least 15
detected subhalos, thus discarding pairs with halos with the lowest
mass.
We end up with a total of 20 pairs that fulfill these criteria,
Appendix A shows the physical  properties (stellar masses, maximum
circular velocities, radial velocities and separation) in those pairs. 
This corresponds to a pair number density of $2 \times10^{-5}$
pairs Mpc$^{-3}$

@@

For a detailed description of the ELVIS project and data we refer the
reader to. 
Here we summarize the elements relevant to our discussion.
The data we use from the ELVIS project comes from the resimulation of
dark matter halo pairs selected in dark matter only cosmological simulations.
The parent cosmological boxes have a cosmology consistent with the
Wilkinson Microwave Anisotropy Probe 7 results.
They used the results from 50 simulation boxes of side lenght $70.4$
Mpc to select pairs with kinematic characteristics similar to the LG.
These selection criteria included the following
\begin{itemize}
\item The virial mass of each host must be in the range 
$1\times
  10^{12} M_{\odot}< M_{vir}<3\times 10^{12}M_{\odot}$ 
\item The total pair mass must be in the range
$2\times
  10^{12} M_{\odot}< M_{vir}<5\times 10^{12}M_{\odot}$ 
\item The center of mass separation is in the range $0.6\leq d\leq1$
  Mpc.
\item The relative radial velocity is negative.
\item No halos more massive than the least massive halo within $2.8$
  Mpc and no halos with $M_{vir}>7\times 10^{13}$ within $7$ Mpc of
  the pairs' center of mass.
\end{itemize}

This corresponds to a pair number density of $8 \times10^{-6}$ pairs
Mpc$^{-3}$, this is a factor $2.4$ lower than the pair number density
we find in Illustris-1.
There were a total of 146 pairs that met those criteria, but only $12$
were chosen for resimulation. 
Additionally, the selected pairs have a relative tangential velocity
less than $75$ \kms.

@@

This compact description allows us to generate samples consistent with
the simulations used in their construction.
Finally, we use those generated samples to estimate how commoon are
the deviations from sphericity that we measure in the observational
data.
